troubleshooting

### 2025-01-28 README.Rmd
Added limma based statistics.

@@

Lastly, *mspms* takes advantage of iceLogos ([Colaert, N. et al. Nature Methods 6,
786-787 (2009)](http://www.ncbi.nlm.nih.gov/pubmed/19876014)) to viusalize
overrepresented amino acid motifs relative to a background set by implementing
components of the Java software in R.

@@

We provide a user-friendly implementation of this statistical test as follows:

@@

Please note that statistical analyses are one of the strengths of the
Bioconductor project and several packages provide alternative statistical
approaches that are more flexible than t-tests and could be used with the
QFeatures objects produced by mspms.

This includes packages using empirical Bayesian approaches (see
[limma](https://bioconductor.org/packages/release/bioc/html/limma.html)) and
mixed modelling (see
[msqrob2](https://bioconductor.org/packages/release/bioc/html/msqrob2.html)),
that are suited for proteomics data.

Users are encouraged to use these excellent packages.

>>>>

-   `r BiocStyle::Biocpkg("limma")`: Powerful linear models and 
empirical Bayesian methods for omics data.

@@

Lastly, *mspms* takes advantage of iceLogos ([Colaert, N. et al. Nature Methods
6,786-787 (2009)](http://www.ncbi.nlm.nih.gov/pubmed/19876014)) to visualize
over represented amino acid motifs relative to a background set by implementing
components of the Java software in R.

@@

We recommend that the user now uses a Limma based approach that uses a linear 
modeling and empirical Bayesian approach. This is a approach well suited to 
proteomics data that is powerful, flexible, and fast.

This limma based approach (with stats calculated relative to time 0 for each 
condition) can be utilized as follows:

```{r}
limma_stats <- mspms::limma_stats(processed_qf = processed_qf)
```

Alternatively, we provide a user-friendly implementation of the traditional
t-test approach as follows:

@@
